Evolution of Flare Activity in GKM Stars Younger than 300 Myr over Five Years of TESS Observations

### 2024-01-09 src/tex/ms.tex
updated references

@@

Stellar flares are the radiation component of magnetic reconnection events \citep{}. Such events are readily seen on the Sun \citep{}, particularly now as we enter a maximum in the solar cycle \citep{}. Such events can be used to understand the magnetic activity of other stars \citep{}. Additionally, by studying stellar flares we can understand how these short-duration events may impact exoplanet evolution \citep{}. While we cannot angularly resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events. Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g. coronal mass ejections \citep{} or proton beams \citep{}. They can also inform our understanding of stellar plasma is displaced during these events \citep{}.

>>>>

\correspondingauthor{Adina~D.~Feinstein;\\ \twitter{afeinstein20}; \github{afeinstein20}} \email{adina.feinstein@lasp.colorado.edu}

@@

Stellar flares are the radiation component of magnetic reconnection events \citep{benz10}. Such events are readily seen on the Sun \citep{carrington1859, lu91, fletcher11}, particularly now as we enter a maximum in the solar cycle \citep{webb94}. Such events can be used to understand the magnetic activity of other stars \citep{feigelson99, berdyugina05, kowalski10, feinstein22_criticality}. Additionally, by studying stellar flares we can understand how these short-duration events may impact exoplanet evolution \citep{france16, guenther19_flares, chen21}. While we cannot angularly resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events. Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g. coronal mass ejections \citep{argiroffi19, vida19} or proton beams \citep{orrall76, woodgate92}.
